No time for dead time - Use the Fourier amplitude differences to normalize dead time-affected periodograms

### 2017-12-15 paper/deadtime.tex
Merge conflicts solved, comments in green addressed (not in Fig. 4 yet)

\begin{figure*}
    \plotone{four_qpos.eps}
    \caption{Periodograms and cospectra from a simulation with four Lorentzian features (at 50, 200, 300 and 400 Hz) with 40-Hz full with at half maximum (FWHM). 
    We plotted and fitted periodograms and cospectra before and after applying a 2.5\,ms dead time filter
    The total \rms before dead time was 40\% and the incident photon flux 400 ct/s. 
    As can be seen from the best-fit curves, there is no significant difference between FAD-normalized and deadtime-free periodograms and cospectra (the curves overlap exactly).
    For comparison, we also plot the cospectrum without FAD (pink), showing very different amplitudes for the four Lorentzians, due to dead time.
    }
    \label{fig:pds}
\end{figure*}

@@

\subsection{Simulation results and discussion}\label{sec:caveat}
\begin{figure*}
    \plotone{errors.pdf}
    \caption{Relative overestimation of FAD with respect to \rms, versus \rms, as calculated from the cospectrum.  
    We encoded in the color the  the incident rate (Top) and the frequency of the feature.
    From this visualization we see two regimes: below $\sim$40\% fractional \rms, the errors are dominated by statistical errors. 
    These errors will simply decrease when we average more data, as we expect from statistical errors.
    Over $\sim$40\% fractional \rms, the errors are significantly skewed towards an overestimation of the \rms, and this is 
    clearly truer when the incident rate \textit{and} the \rms are high, and the frequency relatively low (as can be seen by the fact that the distribution of black points in both plots is more skewed towards positive values). }
    \label{fig:errors}
\end{figure*}

>>>>

\begin{figure*}
    \plotone{four_qpos.eps}
    \caption{Periodograms and cospectra from a simulation with four Lorentzian features (at 50, 200, 300 and 400 Hz) with 40-Hz full with at half maximum (FWHM). 
    We plotted and fitted periodograms and cospectra before and after applying a 2.5\,ms dead time filter
    The total \rms before dead time was 40\% and the incident photon flux 400 ct/s. 
    There is no significant difference between FAD-normalized and deadtime-free periodograms and cospectra, that are almost indistinguishable (note also the agreement between all best-fit Lorentzians).
    For comparison, we also plot the cospectrum without FAD (pink), showing very different amplitudes for the four Lorentzians, due to dead time.
    }
    \label{fig:pds}
\end{figure*}

@@

\subsection{Simulation results and discussion}\label{sec:caveat}
\begin{figure*}
    \plotone{errors.pdf}
    \caption{Relative overestimation of FAD with respect to \rms, versus \rms, as calculated from the cospectrum.  
    We encoded in the color the  the incident rate (Top) and the frequency of the feature.
    From this visualization we see two regimes: below $\sim$40\% fractional \rms, the errors are dominated by statistical errors. 
    These errors will simply decrease when we average more data, as we expect from statistical errors.
    Over $\sim$40\% fractional \rms, the errors are significantly skewed towards an overestimation of the \rms, and this is 
    clearly truer when the incident rate \textit{and} the \rms are high, and the frequency relatively low (as can be seen by the fact that the distribution of darker points in both plots is more skewed towards positive values). }
    \label{fig:errors}
\end{figure*}
